RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-08-05 review/response.tex

\begin{letter}{%
		Guest Editors\\
		IEEE Journal on Selected Areas in Communications
	}
	\opening{Dear Editors and Reviewers,}
	Thank you for giving us the opportunity to submit a revised version of ``RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface''.
	We would like to express our sincere gratitude to you for the valuable comments and suggestions, which helped us improve the quality of the manuscript significantly.
	Below, we prepare a point-to-point response and describe all the changes made to the manuscript.
	We hope that the revisions and clarifications make the manuscript meet the standards of JSAC publications.
	\closing{Yours sincerely,}
\end{letter}

\begin{reviewer}
	This paper introduces the concept of RIScatter, a unified architecture that combines Backscatter Communication (BackCom) and Reconfigurable Intelligent Surface (RIS) technologies, where the scatter nodes can modulate their own information and in the same time manipulate the wireless channel based on the information source, channel state information (CSI), and quality of service (QoS). The achievable primary-total-backscatter rate region in a single-user multi-node RIScatter system is investigated by designing the input distribution at scatter nodes, the active beamforming at the Access Point (AP), and the energy decision regions at the user. Numerical results show that RIScatter nodes can effectively utilize the scattered paths, enabling seamless transitions between backscatter modulation and passive beamforming techniques.

	Although the paper presents a novel idea and tackles an interesting problem, it requires great effort to improve the presentation, the language, and the mathematical derivations. Detailed comments are given as follows:

	\point The abstract and the number of keywords exceed the specified authorized limit. Please check IEEE JSAC guidelines.
	\reply {We apologize for the mistake. The abstract and keywords have been refined to meet the specifications.}

@@

	\point The manuscript contains multiple grammatical errors and unclear sentences that require correction. Please revise the manuscript for improved clarity. For instance, in the first paragraph of Section II, Subsection B, the sentence "It is assumed that the signal reflected by two or more times is negligible" is not clear.
	\reply {We have thoroughly revised the manuscript to address the grammatical errors and improve sentence clarity. The example sentence has been revised to ``It is assumed that the signal going through two or more RIScatter nodes is too weak to be received by the user.''}

	\point Please consider defining all acronyms (e.g., MRC) and all the notations in Section I (e.g., the mutual information, probabilities, etc.,).
	\reply {Thank you for the suggestion and we understand it can be very difficult for readers to keep track of all acronyms and notations throughout the paper. Due to the space limitation, the list is not included but have carefully defined all acronyms and notations before their first usage. We appreciate your understanding in this matter.}

	\point Please ensure that all variables and symbols are properly defined and explained before their usage (e.g., $P$, $\sigma_1^2, \ldots, \sigma_L^2$, etc.). Also, $\mathbf{h}_E^H$ in eq. (46) is used without prior definition.
	\reply {The issue has been addressed in the revised manuscript. $\mathbf{h}_E^H$ in eq. (46) should be $\mathbf{h}^H$.}

	\point Please ensure consistency with the notation introduced in Section I throughout the manuscript. For instance, in Section II, Subsection B, after eq. (4b), the dimensions for $\mathbb{I}$ are not defined.
	\reply {We have revised the manuscript to ensure consistency with the notation introduced in Section~\ref{m-sc:introduction}. In this example, $\alpha_k \in \mathbb{I}$ refers to $\alpha_k \in \mathbb{I}^1$ and the $1$ was omitted for brevity.}

@@

	\point The expression in eq. (1) represents the conjugate of the reflection coefficient, not the reflection coefficient itself.
	\reply {After a careful investigation, we found there are three different definitions for the reflection coefficient in the literature:
		\begin{enumerate}
			\item $\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z}$ in overview papers \cite{VanHuynh2017,Liang2022};
			\item $\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z^*}$ in BackCom paper \cite{Boyer2014};
			\item $\Gamma_m^* = \frac{Z^* - Z_m}{Z + Z_m}$ in RF paper \cite{Hansen1989},
		\end{enumerate}
		where $Z_m$ is the load impedance at state $m$ and $Z$ is the antenna impedance.
		Unfortunately, we are not microwave engineering experts and have to guess that they may choose different parties (antenna and space) as reference. In the current version, we have not made any change to eq. (1) but would be grateful to hear your opinion on this issue.}

	\point It is unclear what is meant by relative QoS. Additionally, there is a lack of clarity regarding the derivation of eqs. (17-19) and how the relative QoS of the primary link is incorporated in those equations. The defined expressions should be clearly explained and justified. Please provide additional details and reasoning.
	\reply {We apologize for the confusion caused by poor wording. QoS refers to the relative priority of the primary link, and it should be either ``QoS'' or ``relative priority''. We have added footnote \ref{m-fn:qos} on this. Besides, the information theory subsection (including the derivation of eqs. (17-19)) has been rewritten and incorporated into Section~\ref{m-sc:system_model} with proper explanation. We also modified Remark \ref{m-re:dynamic_passive_beamforming} and added Remark \ref{m-re:independent_encoding} to clarify the derivation of achievable rates. Please see page~\pageref{m-re:dynamic_passive_beamforming}--\pageref{m-eq:weighted_sum_mutual_information} for details.}

@@

	\point Is the BCD algorithm convergent for the optimization problem (20)?
	\reply {The BCD algorithm is convergent for the optimization problem (20), since the input distribution and active beamforming subproblems converge and the thresholding subproblem attains global optimality. This argument has been added prior to the convergence results in Fig.~\subref*{m-fg:wsr_convergence}.}

@@

	\point In Figure 7, it is unclear why the KKT, PGD, and BCD algorithms are plotted separately since the BCD algorithm encompasses both the KKT and PGD algorithms. If there is a specific reason for displaying them separately, please provide a justification to enhance the understanding of the reader. Additionally, please provide the unit for the weighted sum rate axis.
	\reply {In company with BCD, we also plotted the convergence results of KKT and PGD algorithms to show how much performance gain is provided by solving each subproblem (over the initialization method specified in the previous paragraph). We have justified this in Section~\ref{m-sc:convergence}. The unit of the y axis of Fig.~\ref{m-fg:distribution_weights} has been specified as bit/s/Hz.}

	\point Is the decoding of the backscatter information based on an energy detector reliable in this case, especially with high-order modulation or large number of scatter nodes? In other words, can the user in practice decode the backscatter information especially in the presence of the noise and signal variations due to the fading or the interference, etc.?
	\reply {The energy detector is a simple and practical method for backscatter information decoding, and its reliability is improved by the adaptive input distribution and thresholding design. With high-order modulation or large number of scatter nodes, its performance can be further enhanced by increasing the spreading factor $N$ or using stronger error correction codes with lower code-rate. In practice, the user can decode backscatter nodes ranging from few to hundreds of meters in the presence of noise and interference, and the backscatter throughput can reach few Kbps to tens of Mbps. We have added footnote \ref{m-fn:energy_detector} on this issue, and the reviewer is referred to Table II in \cite{Wu2022e} for more details.}

	\point In Section III, the aim is to characterize the primary-total-backscatter rate region where the user retrieves both the backscatter information and the primary message. Why is the weighted sum mutual information maximized with respect to only the input distribution of the backscatter information and not jointly with respect to the input distribution of the primary message `s' as well? In other words, is the choice of $s \sim \mathcal{CN} (0,1)$ optimal?
	\reply {This is indeed a very good question. The choice of $s \sim \mathcal{CN} (0,1)$ is generally not optimal for weighted sum mutual information. To the best of our knowledge, the optimal primary distribution in this case remains an open issue, but some insights were given in these papers:
		\begin{itemize}
			\item If there is no direct link and the node is with \emph{average} power constraint, then the optimal distribution for \emph{weighted sum mutual information} requires a time-sharing between these modes \cite{Pillai2011}:
			\begin{itemize}
				\item $s$ follows zero-mean Gaussian distribution and $x$ is a constant;
				\item $x$ follows zero-mean Gaussian distribution and $s$ is a constant;
				\item $s$ and $x$ equal 0.
			\end{itemize}
			\item If there is no direct link and the node is with \emph{peak} power constraint, then the optimal distribution for \emph{sum mutual information} is not unique, for example \cite{Zhang2023} (came out after our submission):
			\begin{itemize}
				\item $s$ follows zero-mean Gaussian distribution and $x$ is a constant;
				\item $s$ follows Rayleigh distribution and $x$ follows uniform distribution on $[0, 2 \pi)$;
			\end{itemize}
		\end{itemize}
		Despite not optimal, the assumption of Gaussian primary source and finite-support backscatter source are relatively practical and widely adopted in relevant literatures. We have added Remark~\ref{m-re:non_gaussian} on this, but intentionally avoided the discussion of optimal distribution, since it is beyond the scope of this paper and may confuse the readers. We appreciate your understanding in this matter.}

@@

	\point In Section IV, Subsection B, it is stated that the RIS always ensures constructive superposition of direct and scattered components which is not true. The RIS can also add those components destructively which could be used for example to enhance the physical layer security of a system in the presence of an eavesdropper.
	\reply {We apologize for the oversight. The argument has been modified to ``Here, RIS ensures constructive superposition of direct and scattered components.''}
\end{reviewer}

\begin{reviewer}
	The paper studies the achievable rates for both primary transmission and backscatter information, assuming a Gaussian distribution for primary transmission and $K$ tags (with $M$ loads each) and a single source-destination primary link; the authors assume full CSI knowledge and formulate a mutual information maximization problem, with probability distribution of loads per tag as a function to be optimized (in conjunction with beamforming weights for the multi-antenna transmitter and energy thresholds for the energy-based detector for the backscatter information). The problem is non-convex and challenging, and the authors revert to a series of approximations to relax it and offer a solution. The methodology is interesting in two ways: a) the authors do not employ SIC, but instead focus first on the tags' (weak) information signal, since its knowledge renders the detection of the primary information as a simple coherent detection problem, and b) borrow techniques from the discrete memoryless MAC/discrete memoryless thresholding channel literature, in order to calculate the average rate of the backscattered information.

@@

	The authors balance rate of primary transmission with rate of backscattered tags in a unified, user-controlled way and offer comparison results with prior art in the field (e.g., bistatic backscatter, where no primary link information is present, ambient backscatter, symbiotic (cooperative) ambient backscatter and RIS). Of particular importance is the fact that the authors have modeled both small-scale (through Rice) and large-scale (through distance) fading link parameters, typically omitted in many comm theory papers, even though backscattered links are operating in the presence of the much stronger primary link.

	Overall, the methodology and overall presentation is rigorous and deserves further attention. Having said that, the following remarks are offered:

	\point CSI estimation impact: the notion of full and perfect CSI knowledge is a very strong assumption; the authors do point at footnote 4, page 8 (single column version) to CSI estimation literature. However, CSI estimation for ambient backscatter employs several assumptions and simplifications and it is not perfect or ideal. The authors should perhaps study in terms of simulations the impact of imperfect CSI and necessary degrees of freedom (for channel estimation) on the achieved rates, carefully taking into account the tag(s) small SNR as well as the primary link much stronger SNR.
	\reply {We agree with the reviewer that the assumption of perfect CSI is very strong. Fast and accurate acquisition of cascaded CSI can be challenging especially when the backscatter SNR is weak and/or the number of nodes is large. To investigate the impact of CSI estimation error on the system performance, we have applied the proposed algorithms to an imperfect CSI model, where the cascaded channel of node $k$ is estimated as
		\begin{equation}
			\hat{\boldsymbol{h}}_{\text{C},k} = \boldsymbol{h}_{\text{C},k} + \tilde{\boldsymbol{h}}_{\text{C},k},
		\end{equation}
		$\tilde{\boldsymbol{h}}_{\text{C},k}$ is the estimation error with entries following i.i.d. CSCG distribution $\mathcal{CN}(0, \iota \Lambda_\text{C})$, $\iota$ is the relative estimation error, and $\Lambda_\text{C}$ is the cascaded path loss.
		In Fig.~\ref{fg:region_csi}, it is observed that the channel estimation error mainly affects the backscatter rate.
		When $\iota$ increases from \num{0} to \num{0.2}, the maximum total backscatter rate decreases by \qty{20}{\percent}.
		This is because the energy detector is sensitive to the DMMAC and thus $\hat{\boldsymbol{h}}_{\text{C},k}$.
		On the other hand, a small estimation error may be insufficient to change the optimal passive beamforming state (especially for a small $M$) and the primary rate is almost unchanged in this case.
		We have added the result and discussion on imperfect CSI in page~\pageref{m-fg:region_csi}.
	}
	\begin{figure}[!t]
		\centering
		\resizebox{0.48\columnwidth}{!}{
			\input{../assets/simulation/region_csi.tex}
		}
		\caption{
			Average primary-total-backscatter rate regions vs imperfect cascaded CSI.
		}
		\label{fg:region_csi}
	\end{figure}

	\point Modeling assumptions: the overall model is based on Gaussian codebooks for the primary link and lack of structural mode for backscattering; the latter is assumed absorbed by the channel parameters (Section II.A), while the tags are assumed with a demodulator/receiver of the primary information; it is also assumed that both full CSI and reflection efficiency parameters $\{\alpha_k\}, k \in \{1, 2, \ldots, K\}$ are known for all tags, while each tag is equipped with a receiver/demodulator (for the primary information). The reviewer believes that the structural mode cannot be absorbed by the channel parameters, since it offers a DC term, while there is no practical way to estimate separately the cascaded channel from the reflection efficiency; moreover, receivers in tags either increase the complexity or reduce the tag's sensitivity, especially when envelope detectors are used (as in Fig. 3). Moreover, the assumption for perfect symbol-level synchronization between tags and source, or the integer ratio between tags and source symbol duration is also very strong. Some discussion on the above is necessary, while some thoughts on non-Gaussian codebooks and how the methodology could be extended is perhaps important.
	\reply {Your valuable comments on scatter modeling and codebook design are very much appreciated. When the transmitted waveform is a continuous carrier wave (CW) that carries no information, the structure mode component is also a CW. After downconversion, its contribution is indeed modelled as a DC offset \cite{Boyer2014}. However, when the transmitted waveform is a modulated signal, the structure mode component is proportional to the modulated signal, and its contribution can thus be absorbed in the environment multipath \cite{Thomas2012,Liang2020}. When estimating the cascaded CSI, the reflection efficiency $\{\alpha_k\}$ can be set to some pre-determined values, such that the cascaded channels can be separated from the reflection efficiency. We agree with the reviewer that adding integrated receivers will increase the complexity and reduce the sensitivity of the nodes. The aim is to coordinate the nodes with the active source and to acquire the optimized input distributions, instead of decoding the primary information dedicated for the user. Thus, those receivers can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity. Besides, the assumption of perfect symbol-level synchronization and integer spreading ratio are made to simplify the achievable rate analysis, and they have been widely adopted in relevant literatures \cite{Liang2020,Ding2020,Long2020a,Guo2019b,Han2021,Zhang2022}. If they are not satisfied, some penalty can be introduced to the achievable rate and it is left for future work. We have incorporated the above discussions in footnote \ref{m-fn:integrated_receiver}.}

	\point Independent distributions across tags: (10) assumes independence among distributions of tag loads across tags; IV.D.1 talks about joint nodes encoding; pls clarify. In addition, some more discussion is needed at IV.C and Fig. 9; for $\rho=1$, i.e., primary transmission maximum prioritization, Fig. 9 shows that only one load (out of 4) should be used. The reviewer was puzzled by this. Perhaps, values of the loads used in the simulations and respective reflection coefficients should be explicitly offered, in conjunction with more discussion regarding the wireless channel impact. When the channel changes, one would expect the distribution of the tags' loads to be sensitive on channel statistics.
	\reply {We apologize for the confusion caused by poor writing. The achievable rate analysis and the algorithms are provided for the most general case where all nodes encode independently. When multiple nodes are co-located, they can jointly encode by designing the joint probability $p(x_{m_{\mathcal{K}}})$ directly. This formulates an augmented backscatter source and becomes a special case of independent encoding. In the revised manuscript, we have clarified the above points in Remark~\ref{m-re:augmented_source} and footnote~\ref{m-fn:joint_encoding}. Regarding the observation in Fig. 9, please note that one state corresponds to one equivalent load (and one reflection coefficient). In this case, there is exactly one reflection coefficient (corresponds to state 3) that maximizes the primary SNR, and it should be used with probability 1 to maximize the primary rate. Instead of explicitly designing the value of load impedance, we assume that they have been designed to fulfill the reflection coefficient codebook. The node input distribution (not the reflection coefficient codebook) is indeed adaptive to CSI, as mentioned in Section~\ref{m-sc:input_distribution}. We have clarified the above points in the revised manuscript.}

	\point All simulation results and respective optimization solutions are offered with relatively small number of K and M; some discussion on ways to extend the methodology for larger networks and loads should be helpful.
	\reply {Thank you for the suggestion. The main limitations for massive RIScatter are the energy detection and the dynamic programming algorithm. For $K$ nodes each with $M$ states, there are a total of $L = M^K$ energy decision regions to design. The candidate threshold set $\mathcal{T}$ should be even finer, which results in a very fast growth of the computational complexity ($\mathcal{O}\bigl(L^2(\mathrm{card}(\mathcal{T})-L)\bigr)$ for SMAWK and $\mathcal{O}\bigl(\mathrm{card}(\mathcal{T})L\log(\mathrm{card}(\mathcal{T})L)\bigr)$ for bisection). To support massive RIScatter networks with large number of nodes and states, one possible future direction is to consider backscatter detection over the received signal domain rather than energy domain, where multi-antenna \cite{Liu2022c} and learning-based approaches can be promising. We have added this to Section~\ref{m-sc:conclusion} of the revised manuscript.}

### 2023-08-05 main.tex
:speech_balloon: Update response

	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader, to perform passive beamforming (but no backscatter modulation) towards a legacy user at a different frequency.
	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	Those problems are addressed in this paper and the contributions are summarized below.

	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission, simultaneously modulating their information and engineering the wireless channel.
	A co-located receiver cooperatively decodes both coexisting links.
	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.}.
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the practical receiver and input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

@@

		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user. The node receiver can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
		% The detail will be covered in Section~\ref{st:system_model}.
	\end{subsection}

	\begin{subsection}{System Model}
		\label{se:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.7\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{riscatter_network.pdf_tex}
			}
			\caption{A single-user multi-node RIScatter network.}
			\label{fg:riscatter_network}
		\end{figure}
		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
		All nodes have $M$ available reflection states.
		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.

@@

		\begin{subsubsection}{Average Noise Power}
			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
			It shows the proposed practical semi-coherent backscatter energy detection is suitable for a wide range of noise levels.
			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to maintain the backscatter \gls{snr} for better energy detection performance.
		\end{subsubsection}

>>>>

	On the other hand, static \gls{ris} that employs fixed reflection pattern per channel block has been extensively studied in wireless communication, sensing, and power literature \cite{Wu2018,Zhang2019a,Lin2022,Liu2022,Feng2022,Zhao2022}.
	Dynamic \gls{ris} performs time sharing between different phase shifts and introduces artificial channel diversity within each channel block.
	The idea was first proposed to fine-tune the \gls{ofdm} resource blocks \cite{Yang2020}, then extended to the downlink power and uplink information phases of \gls{wpcn} \cite{Wu2021,Wu2021d,Hua2022a}.
	However, dynamic \gls{ris} carries no information because the reflection state at a specific time is known to the receiver.
	\gls{ris} can also be used as an information source, and prototypes have been developed for \gls{psk} \cite{Tang2019a} and \gls{qam} \cite{Dai2020a}.
	From an information-theoretic perspective, the authors of \cite{Karasik2020} reported that joint transmitter-\gls{ris} encoding achieves the capacity of \gls{ris}-aided finite-input channel, and using \gls{ris} as a naive passive beamformer to maximize the receive \gls{snr} is generally suboptimal.
	This inspired \cite{Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hu2021b,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} to combine passive beamforming and backscatter modulation in the overall \gls{ris} design.
	In particular, \emph{symbol level precoding} maps the information symbols to the optimized \gls{ris} coefficient sets \cite{Liu2019d,Bereyhi2020}, \emph{overlay modulation} superposes the information symbols over a common auxiliary matrix \cite{Xu2020b,Zhang2021d,Hu2021b,Hua2022}, \emph{spatial modulation} switches between the reflection coefficient sets that maximize \gls{snr} at different receive antennas \cite{Basar2020,Ma2020a,Yuan2021}, and \emph{index modulation} employs dedicated reflection elements (resp. information elements) for passive beamforming (resp. backscatter modulation) \cite{Hu2021a}.
	Those \gls{ris}-based backscatter modulation schemes incur advanced hardware architecture and high optimization complexity.
	In contrast, \cite{Vardakis2023} exploits commodity \gls{rfid} tags, powered and controlled by a software-defined radio reader, to perform passive beamforming (but no backscatter modulation) towards a legacy user at a different frequency. \label{cm:2.5}
	% The authors demonstrated the feasibility of using batteryless devices to adaptively enhance the \gls{snr} of a primary link, but did not consider backscatter modulation at.
	Most relevant literature considers either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} that is impractical for low-power nodes, or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} that does not fully exploit the \gls{csi} and properties of active-passive coexisting networks.
	Those problems are addressed in this paper and the contributions are summarized below.

	\emph{First,} we propose RIScatter as a novel protocol that unifies \gls{bc} and \gls{ris} by adaptive reflection state (backscatter input) distribution design.
	The concept is shown in Fig.~\subref*{fg:riscatter} where one or more RIScatter nodes ride over an active transmission, simultaneously modulating their information and engineering the wireless channel.
	A co-located receiver cooperatively decodes both coexisting links.
	Each reflection state is simultaneously an information codeword and a passive beamforming codeword.
	The reflection pattern over time is semi-random and guided by the input probability assigned to each state.
	This probability distribution is carefully designed to incorporate the backscatter information, \gls{csi}, and \gls{qos}\footnote{\gls{qos} refers to the relative priority of the primary link.\label{fn:qos}}.
	Such an adaptive channel coding boils down to the degenerate distribution of \gls{ris} when the primary link is prioritized, and outperforms the uniform distribution of \gls{bc} (by accounting the \gls{csi}) when the backscatter link is prioritized.
	Table~\ref{tb:scattering_applications} compares RIScatter to \gls{bc} and \gls{ris}.
	However, two major challenges for RIScatter are the practical receiver and input distribution design.
	This is the first paper to unify \gls{bc} and \gls{ris} from the perspective of input distribution.

@@

		RIScatter nodes can be implemented, for example, by adding an integrated receiver\footnote{The aim is to coordinate the node with the active source and to acquire the optimized input distribution, instead of decoding the primary information dedicated for the user. The node receiver can be implemented using very simple circuits or even integrated with the rectifier \cite{Kim2021a} to reduce cost and complexity.\label{fn:integrated_receiver}} \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		The block diagram, equivalent circuit, and scatter model are illustrated in Fig.~\ref{fg:riscatter_node}.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		% To exploit the benefits of RIScatter, we also propose a low-complexity receiver that semi-coherently decodes the backscatter link, re-encodes to recover the reflection pattern, and coherently decodes the primary link.
		% The detail will be covered in Section~\ref{st:system_model}.
	\end{subsection}

	\begin{subsection}{System Model}
		\label{sc:system_model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.7\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{riscatter_network.pdf_tex}
			}
			\caption{A single-user multi-node RIScatter network.}
			\label{fg:riscatter_network}
		\end{figure}
		As shown in Fig.~\ref{fg:riscatter_network}, we consider a RIScatter network where a $Q$-antenna \gls{ap} serves a single-antenna user and $K$ nearby dispersed or co-located RIScatter nodes.
		All nodes have $M$ available reflection states.
		In the primary point-to-point system, the \gls{ap} transmits information to the user over a multipath channel\footnote{It is assumed the primary symbol duration is much longer than multipath delay spread (i.e., no inter-symbol interference).} enhanced by RIScatter nodes.
		In the backscatter multiple access system, the \gls{ap} acts as carrier emitter, the RIScatter nodes modulate over scattered signal, and the user jointly decodes all node messages.\footnote{It is assumed the signal going through two or more RIScatter nodes is too weak to be received by the user.}
		For simplicity, we consider a quasi-static block fading model and focus on a specific channel block where the \gls{csi} remains constant.
		Denote the \gls{ap}-user direct channel as $\boldsymbol{h}_{\text{D}}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the \gls{ap}-node $k \in \mathcal{K} \triangleq \{1,\ldots,K\}$ forward channel as $\boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$, the node $k$-user backward channel as $h_{\text{B},k}$, and the cascaded \gls{ap}-node $k$-user channel as $\boldsymbol{h}_{\text{C},k}^\mathsf{H} \triangleq h_{\text{B},k} \boldsymbol{h}_{\text{F},k}^\mathsf{H} \in \mathbb{C}^{1 \times Q}$.
		We assume the direct and cascaded \gls{csi} are available at the \gls{ap} and user\footnote{The cascaded \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel \cite{Jin2021a} approaches for dispersed nodes, or group-based \cite{Zheng2019} or hierarchical \cite{You2019} approaches for co-located nodes.}.

@@

		\begin{subsubsection}{Average Noise Power}
			Fig.~\subref*{fg:region_noise} depicts the impact of average noise power $\sigma_v^2$ on average rate regions.
			Note that the noise influences both primary and backscatter \gls{snr}.
			% It shows the proposed adaptive energy detector is suitable for a wide range of noise levels.
			When $\sigma_v^2$ relatively high, one can choose a larger $N$ to improve the energy detection \gls{snr}.
		\end{subsubsection}
